What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2024-08-21 group-d/E4-analysis-calibration.Rmd
E2 and E3 materials sections, calibration plots
E4 edits (add corr plot, wordsmithing)

```
```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
  geom_point()+
  geom_smooth(method = "lm")
```

@@

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm")
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %). 
The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration

>>>>

```{r, eval = F}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = modifier))+
  geom_point()+
  geom_smooth(method = "lm")
```

@@

```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm") +
  labs(x="Calibration Score", y="Bias Effect") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%). 
The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure \ \@ref(fig:E4-calib-corr-plot)).

### 2024-08-21 manuscript.Rmd
E4 edits (add corr plot, wordsmithing)

57 participants were paid \$2.50 for their participation. A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power. Note that the original study had a sample size of 24.

### Materials

The images and audios presented to the participants were the same
stimuli used in the original study (available here <link>). The critical
trials were divided into modifier-biased, instrument-biased, and
equibiased conditions, and the filler trials did not contain ambiguous
instructions. Two lists of critical trials were made with different verb
and instrument combinations (e.g., "rub" could be paired with "panda"
and "crayon" in one list and "panda" and "violin" in the second list).
Within each list, the same verb was presented twice but each time with a
different target instrument and animal. The lists were randomly assigned
to the participants to make sure the effects were not caused by the
properties of the animal or instrument images used. The list of verbs
used can be found in Appendix A of the original study.

@@

### Comparison to in-lab data

@@

As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier, instrument or equi). For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes). This pattern was stronger for those who achieved higher calibration accuracy and when quadrant-based ROIs were used compared to image-based ROIs.

>>>>

Fifty-seven participants were paid \$2.50 for their participation. A sample size of 60 was initially chosen (but not reached in time) because we wanted to replicate the experiment with greater statistical power. Note that Ryskin et al. (2017) Experiment 1 had a sample size of 24.

The images and audios presented to the participants were the same
stimuli used in the original study. The critical
trials were divided into modifier-biased, instrument-biased, and
equibiased conditions, and the filler trials did not contain ambiguous
instructions. Two lists of critical trials were made with different verb
and instrument combinations (e.g., "rub" could be paired with "panda"
and "crayon" in one list and "panda" and "violin" in the second list).
Within each list, the same verb was presented twice but each time with a
different target instrument and animal. The lists were randomly assigned
to the participants to make sure the effects were not caused by the
properties of the animal or instrument images used. There were 54 critical trials per list (3 verb conditions x 9 verbs per condition x 2 presentations) and 24 filler trials. The list of the 27 verbs used, along with their verb bias norms, can be found in Appendix A of the original study.

@@

@@

As in @ryskinVerbBiasesAre2017 and @snedekerDevelopingConstraintsParsing2004a, listeners' gaze patterns during sentences with globally ambiguous syntactic interpretations differed depending on the bias of the verb (i.e., modifier-, instrument-, or equi-). For modifier-biased verbs, participants looked more quickly at the target animal and less at the potential instrument than for instrument-biased verbs (and equi-biased verbs elicited a gaze pattern between these extremes). This pattern was stronger for those who achieved higher calibration accuracy and when quadrant-based ROIs were used compared to image-based ROIs.
